%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Academic Involvement}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

\cventry
    {Quantitative Analyst} % Job title
    {
    \href{https://fonds-bni.hec.ca/}{BNI-HEC Investment Funds}} % Organisation
    {Montreal, Canada} % Location
    {September 2022 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Managed a $\$$5 million portfolio under the supervision of National Investment Bank. Member of the R$\&$D team.}
        \item {Develop quantitative investment models to support both strategic and tactical portfolios.}
        \item {Create systems required for the proper functioning of the Fund (dashboards, weekly/monthly reports, performance attribution, risk analysis, etc.)}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\href{https://www.hec.ca/salledesmarches/activites/club-trading/}{Vice President Research}} % Organisation
    {{Trading Club}} % Project
    {Montreal, Canada} % Location
    {August 2023 - May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Management of a team of 4 students to reproduce research papers on coastline trading (High Frequency Strategy on FX market) and energy trading (modelling DA-RT spikes of electricity).}
        \item {Development and backtesting of strategies in Python under the supervision of Associate Professor Saad Ali-Khan.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {\href{https://www.hec.ca/cours/detail/?cours=ECON20851}{Teaching Assistant Intermediate Microeconomics }} % Organisation
    {\href{https://www.hec.ca/iea/}{Department of Applied Economics}} % Project
    {Montreal, Canada} % Location
    {August 2021 - January 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{Assistant to the full professor \href{https://www.hec.ca/profs/pierre-carl.michaud.html}{Pierre-Carl Michaud.}}
        \item {Correction of tutorials, review of lecture notes, consultation with students, answering questions, creating exercises.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {\href{https://www.hec.ca/cours/detail/?cours=MATH10602}{Teaching Assistant Mathematics Preparatory Year}}
    {\href{https://www.hec.ca/mqg/}{Department of Decision Sciences}} % Organisation
    {Montreal, Canada} % Location
    {August 2021 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item{Assistant to the master teacher \href{https://www.hec.ca/profs/fatiha.kacher.html}{Fatiha Kacher.}}
        \item {Correction of exams and tutorials, consultation hours for students.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Vice President Education}
    {\href{https://www.csdschec.com/}{Data Science Committee}} % Organisation
    {Montreal, Canada} % Location
    {August 2020 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Realization of a conference named "AI in 2020" gathering more than 40 students and industry professionals.}
        \item {Conducted a "Lunch and Learn" event with Professor David Ardia (Associate Professor, Department of Decision Sciences) to present a research topic on the topic of "Sentometry".}
      \end{cvitems}
    }

%---------------------------------------------------------


\end{cventries}
