%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\newpage
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.hec.ca/programmes/maitrises/maitrise-ingenierie-financiere/}{MSc in Financial Engineering - Thesis}} % Degree
    {\href{https://www.hec.ca/}{HEC Montreal}} % Institution
    {Montreal, Canada} % Location
    {August 2022 - December 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textbf{Thesis:} Gamma Exposure and Intraday Volatility Dynamics in the SPX Options Market -- Analysis of dealer gamma hedging impact on realized volatility using 5-minute options data (2B+ data points, Aug 2020--Jul 2025).}
        \item{\textbf{GPA:} 3.88/4.3. Recipient of the Deloitte M.Sc scholarship and the Jocelyne \& Jean C. Monty scholarship of excellence for academic merit.}
        \item{\textbf{Hackathons:} ConUHacks VIII winning team for National Bank challenge 2024 (1000+ participants). Top 10 finalist at McGill FIAM Portfolio Management Hackathon (66 teams).}
        \item{\textbf{Leadership:} Vice President Research at the Trading Club -- organized workshops on derivatives and systematic trading. R\&D Analyst at BNI-HEC Investment Fund (\$5M AUM) -- conducted equity research and portfolio analysis.}
        \item{\textbf{Courses:} Stochastic Calculus, Derivatives Pricing, Fixed Income Securities, Financial Econometrics, Machine Learning for Finance, Numerical Methods, Risk Management.}
      \end{cvitems}
    }
    
  \cventry
    {\href{https://www.hec.ca/etudiants/mon-programme/baa/specialisations/economie-appliquee-finance-mathematiques.html}{Bachelor's degree in Business Administration | specialization in Mathematics, Finance and Economics}} % Degree
    {\href{https://www.hec.ca/}{HEC Montreal}} % Institution
    {Montreal, Canada} % Location
    {August 2017 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{\textbf{GPA:} 3.8/4.3 for specialization courses. Selective quantitative track combining advanced mathematics, economics, and finance.}
        \item{\textbf{Leadership:} Vice President Education at the Data Science Committee -- organized Python workshops and machine learning seminars.}
        \item{\textbf{Competitions:} RITC Trading Competition participant -- simulated trading in equities and derivatives markets.}
        \item{\textbf{Teaching:} Teaching Assistant for Intermediate Microeconomics (200+ students). Private mathematics tutor (Calculus, Linear Algebra).}
        \item{\textbf{Courses:} Econometrics, Portfolio Management, Options \& Futures, Quantitative Finance, Probabilistic Models, Corporate Finance.}
      \end{cvitems}
    }
    
    \cventry
    {\href{https://admission.umontreal.ca/programmes/mineure-en-mathematiques/}{Minor in Mathematics}} % Degree
    {\href{https://www.umontreal.ca/}{University of Montreal}} % Institution
    {Montreal, Canada} % Location
    {August 2018 - August 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Complementary mathematics program completed concurrently with BBA to strengthen quantitative foundations.}
        \item{\textbf{Courses:} Probability Theory, Mathematical Statistics, Stochastic Processes, Linear Algebra, Multivariable Calculus, Real Analysis, Programming (C/C++).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}