%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

    \cventry
    {Quantitative Researcher}
    {\href{https://greenberg-management.com}{Greenberg Management}}
    {Montreal, Canada}
    {May 2025 - Present}
    {
        \begin{cvitems}
            \item{Develop and optimize systematic trading strategies (Momentum, Volatility Risk Premium, Mean Reversion) across US equities, indices, options, and fixed income markets.}
            \item{Design and implement volatility strategies harvesting the VRP through systematic derivatives trading, achieving \textbf{25\% annualized returns} over a 7-year period with controlled drawdown ($\sim$25\%).}
            \item{Build cloud-based algorithmic trading infrastructure in Python; execute and monitor strategies with 7-figure monthly volume.}
            \item{Collaborate with derivatives trader to systematize discretionary volatility strategies into fully automated trading systems.}
            \item{Conduct quantitative research on options pricing, Greeks dynamics, and market microstructure to enhance signal generation and execution.}
            \item{\textbf{Stack}: Python, cloud infrastructure, options analytics, algorithmic execution, backtesting frameworks, risk management.}
        \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {Quantitative Analyst}
    {\href{https://www2.deloitte.com/ca/en/pages/about-deloitte/articles/home.html}{Financial Engineering \& Modeling - Financial Risk | Deloitte}}
    {Montreal, Canada}
    {October 2024 - June 2025}
    {
        \begin{cvitems}
            \item{Developed and validated credit risk models (PD, LGD, EAD) for major Canadian financial institutions under IFRS 9 and Basel III/IV regulatory frameworks.}
            \item{Led independent model validation engagements: statistical backtesting, sensitivity analysis, stress testing, and regulatory documentation for OSFI compliance.}
            \item{Performed quantitative assessment of model assumptions, calibration methodologies, and discriminatory power using Gini coefficients and KS statistics.}
            \item{Built automated model monitoring dashboards and validation pipelines in Python, reducing manual review time by \textbf{40\%}.}
            \item{Authored technical validation reports and presented findings to senior stakeholders and client risk committees.}
            \item{\textbf{Stack}: Python, R, SQL, statistical modeling, regulatory compliance (IFRS 9, Basel III/IV, OSFI guidelines).}
        \end{cvitems}
    }

%---------------------------------------------------------
   \cventry
    {Quantitative Developer Intern} % Job title
    {\href{https://bnmf.ca}{Global Equity Derivatives R\&D - Structured Products \& Exotics | National Bank Financial Markets}} % Organization
    {Montreal, Canada} % Location
    {May 2023 - December 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item{Developed and deployed SmartBeta strategies (Low Volatility, Momentum) managing \textbf{\$800M AUM} within a \$7B structured products division.}
      \item{Achieved \textbf{\$1M annual cost savings} through strategy optimization and migration from external vendor to internal production systems.}
      \item{Built end-to-end backtesting framework in Python: signal generation, portfolio construction, transaction cost modeling, risk analytics, and performance attribution.}
      \item{Implemented portfolio optimization algorithms with constraints (turnover limits, sector exposure, factor tilts) using convex optimization (cvxpy).}
      \item{Delivered weekly quantitative reports to senior stakeholders; presented strategy performance and risk metrics to trading desk and portfolio managers.}
      \item{Collaborated with structuring and trading teams to integrate quantitative signals into exotic derivatives pricing and hedging workflows.}
      \item{\textbf{Stack}: Python (OOP), Bloomberg Terminal \& API, SQL, AWS (EC2, S3), optimization algorithms, statistical testing.}
    \end{cvitems}
    }

%---------------------------------------------------------

  
  \cventry
    {Data Analyst} % Job title
    {\href{https://www.vidensanalytics.com}{Videns Analytics}} % Organisation
    {Montreal, Canada} % Location
    {April 2020 - June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Designed and delivered data science curriculum (Python, statistics, ML) for \textit{Videns Academy} platform; content adopted by UQAC for university course.}
        \item{Built predictive models and automated reporting pipelines for insurance clients, improving claims analysis and risk assessment workflows.}
        \item{Led consulting engagements in insurance analytics: data cleaning, exploratory analysis, and dashboard development for client decision-making.}
        \item{Promoted from intern to full-time Data Analyst based on project delivery and client satisfaction.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
